---
title: Tuango - RFM Analysis for Mobile App Push Messaging on the post roll-out data
output: html_document
---

* Name:Qiuyi Lu
* GitLab id: rsm-q2lu

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (!exists("r_environment")) library(radiant)
library(tidyverse)
```

<style>
.btn, .form-control, pre, code, pre code {
  border-radius: 4px;
}
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
code, pre, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
}
code {
  color: #c7254e;
  background-color: #f9f2f4;
}
pre {
  background-color: #ffffff;
}
</style>

## Setup

Please complete this Rmarkdown document by answering question 14 in `tuango.pdf` on Canvas (week4/). The code block below loads the data you need for this second Rmarkdown file. Create an HTML file with all your results and answers and push both the Rmarkdown and HTML file to GitLab when you are done. All results MUST be reproducible (i.e., the TA and I must be able to recreate the Notebook/HTML from the Rmarkdown file without changes or errors).

```{r}
## loading the data - this dataset must NOT be changed
tuango <- readRDS("data/tuango_post.rds")


## calculate iq sq index
tuango_post=tuango %>% mutate(
rec_iq=xtile(recency,5),
fre_iq=xtile(frequency,5,rev = TRUE),
mon_iq=xtile(monetary,5,rev=TRUE),
rfm_iq=paste0(rec_iq,fre_iq,mon_iq))

tuango_post <- tuango_post %>% group_by(rec_iq) %>%
  mutate(fre_sq = xtile(frequency, 5, rev = TRUE)) %>%
  ungroup()

## calculate sequential monetary quintiles
 tuango_post<- tuango_post%>% group_by(rec_iq, fre_sq) %>%
  mutate(mon_sq = xtile(monetary, 5, rev = TRUE)) %>%
  ungroup()
 
 tuango_post$rec_sq=tuango_post$rec_iq
 tuango_post=tuango_post%>%mutate(rfm_sq=paste0(rec_sq,fre_sq,mon_sq))
 tuango_post_train=tuango_post %>% filter(training==1)
 tuango_post_test=tuango_post %>% filter(training==0)
 
## conditions
one_more= tuango_post_train[tuango_post_train$ordersize>1,]
ave_amount=sum(one_more$ordersize)/nrow(one_more)
cost_to_push=2.5
margin_on_sales=ave_amount*0.5
breakeven_respon=cost_to_push/margin_on_sales
```

```{r}
mailto_iq=tuango_post_train %>% group_by(rfm_iq_pre) %>% mutate(mailto=mean(buyer=='yes')>breakeven_respon)

mailto_sq=tuango_post_train %>% group_by(rfm_sq) %>% mutate(mailto=mean(buyer=='yes')>breakeven_respon)

mailto_lbiq=tuango_post_train %>% group_by(rfm_iq_pre) %>% mutate(lb=mean(buyer=='yes')-1.64*seprop(buyer=='yes'), mailto=lb>breakeven_respon)

mailto_lbsq=tuango_post_train %>% group_by(rfm_sq) %>% mutate(lb=mean(buyer=='yes')-1.64*seprop(buyer=='yes'), mailto=lb>breakeven_respon)


tuango_perrfm=tuango_post_train %>% filter(buyer=='yes') %>% group_by(rfm_sq) %>% summarise(ave_amount=mean(ordersize)) %>% mutate(breakeven_respon=cost_to_push/(0.5*ave_amount))
response_rate_perrfm=tuango_post_train %>% group_by(rfm_sq) %>% summarise(respon_rate=mean(buyer=='yes'))
tuango_per_rfm=tuango_perrfm %>% left_join(response_rate_perrfm,by='rfm_sq') %>% filter(respon_rate>breakeven_respon) 

```


```{r}
# function 
profit_ROME_calc=function(df,intro){
mailing_cost=nrow(df)*cost_to_push
profit=sum(df$ordersize)*0.5-mailing_cost
ROME=profit/mailing_cost
real_iq=data.frame(intro,profit=profit,ROME=ROME)
}

# independent 
mailed_list=mailto_iq %>% filter(mailto==TRUE) %>% select(rfm_iq_pre)
tuango_test=tuango_post_test %>% filter(rfm_iq_pre %in% mailed_list$rfm_iq_pre)
real_iq=profit_ROME_calc(tuango_test,intro='real_iq')

 
# sq
mailed_list= mailto_sq%>% filter(mailto==TRUE) %>% select(rfm_sq)
tuango_test=tuango_post_test %>% filter(rfm_sq %in% mailed_list$rfm_sq)
real_sq=profit_ROME_calc(intro='real_sq',tuango_test)

# iq_se
mailed_list=mailto_lbiq %>% filter(mailto==TRUE) %>% select(rfm_iq_pre)
tuango_test=tuango_post_test %>% filter(rfm_iq_pre %in% mailed_list$rfm_iq_pre)
real_iq_se=profit_ROME_calc(intro='real_iq_se',tuango_test)

# sq_se

mailed_list=mailto_lbsq %>% filter(mailto==TRUE) %>% select(rfm_sq)
tuango_test=tuango_post_test %>% filter(rfm_sq %in% mailed_list$rfm_sq)
real_sq_se=profit_ROME_calc(intro='real_sq_se',tuango_test) 
 
# per_frm_sq
mailed_list=tuango_per_rfm$rfm_sq
tuango_test=tuango_post_test %>% filter(rfm_sq %in% mailed_list)
real_per_frm_sq=profit_ROME_calc(intro='real_per_frm_sq',tuango_test)

#compare table
real_compare_table=rbind(real_iq,real_sq,real_iq_se,real_sq_se,real_per_frm_sq)
print(real_compare_table)

#profit bar chart:
visualize(
  real_compare_table,
  xvar = "intro",
  yvar = "profit",
  type = "bar",
  labs = list(
    y = "profit", 
    x = "intro"
  ),
  custom = FALSE
)

#ROME bar chart:
visualize(
  real_compare_table,
  xvar = "intro",
  yvar = "ROME",
  type = "bar",
  labs = list(
    y = "ROME", 
    x = "intro"
  ),
  custom = FALSE
)
```


## Question answers


In reality, using sequential FRM yielded highest profit. Second is by using per frm sq.<br/>
In terms of ROME,using independent frm standandard error performed best.
The rankings of profit and ROME are the same as the estimated answer.<br/>
